---
title: "R LADS group 8 Midterm Project"
author: "Thomas"
date: "14-11-2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Possible project

What needs to be done:
* install facebook API package
* get authorization

* find a relevant page in Chinese like BBC (see script below)
* find a post with a lot of comments, maybe something political or racial or whatever
* find comments
* make comments into a corpus/dataframe (see before)
* cut comments with jieba
* make wordclouds






# Set-up

```{r}
library(tidyverse)
library(Rfacebook)
```

# Case study: facebook

  - 到 `https://developers.facebook.com/tools/explorer`

Getting the token, be sure to check all the things you want
```{r}
token <- 'EAACEdEose0cBABGiPygjSO3T3ElgzkuxOXlaVNyASg5EQS3Ux7zTEU26nkhiSjc1PfZAHSUcxYwQNcnwhYZCn4EIoRbXbYWRKjwxCY41lZAGqO6BFuZCZAvAzQSppXtFuIc3epB9ovZABo1xJeHWQ5yQxXGxvZAamFNZAn3jixTZATLfYm3rr9vnUbhUcqnIyYp0k7fZAUXKHWwAZDZD'
```

Checking if we got the right account
```{r}
me <- getUsers("me", token, private_info = TRUE)
#me <- getUsers("me",token=fb_oauth)
me$name
```



```{r}
BBCpage <- getPage(page="bbcnews", token = token, n=50) 
```


- 特定時間的所有貼文

```{r}
BBCpage.2 <- getPage("bbcnews", token = token, n=50, since='2017/10/01', until='2017/10/20')
```

- 哪那一則貼文得到最多的讚?

```{r}
summary <- BBCpage.2[which.max(BBCpage.2$likes_count),]
summary$message
```


- 哪一則得到最多的評論?
```{r}
summary1 = BBCpage.2[which.max(BBCpage.2$comments_count),]

```

- 哪一則貼文最多分享?
```{r}
summary2 = BBCpage.2[which.max(BBCpage.2$shares_count),]
```

- 得到最多讚的貼文的所有按讚者

```{r}
post <- getPost(summary$id[1], token = token, comments = FALSE, n.likes=2000)

```


- 看看究竟是誰（注意個資）

```{r}
likes <- post$likes
head(likes)
```


- 特定貼文的評論

To know what users think about a post, it is important to analyze their comments.
```{r}
post <- getPost(BBCpage.2$id[1], token=token, n.comments=1000, likes=FALSE)
comments <- post$comments
```

- 哪個評論得到最多的讚？

```{r}
comments[which.max(comments$likes_count),]
```

- 最近貼文的心情（需要 tweak）

Facebook has more than a like button. Last year, it launched emoji (emoticons). If a post got 1k likes, it does not mean everyone really loves the comment. The reaction can be happy, sad or angry.

```{r}
post <- getReactions(post=BBCpage.2$id[1], token= token)

```


---

What needs to be done:
* find a relevant page in Chinese like BBC
* find a post with a lot of comments, maybe something political or racial or whatever
* find comments
* cut comments with jieba
* make wordclouds


















